---
title: "Programa de Prevención y Control del Dengue de Campeche"
output: 
  flexdashboard::flex_dashboard:
      theme: united
      social: ["twitter", "facebook", "menu", "github"]
output_dir: libs      
---

```{r setup}

# Step 1. load the library ####
options(shiny.maxRequestSize=30*1024^2)
library(formattable)
library(tmap)
library(rmarkdown)
library(knitr)
library(shiny)
library(flexdashboard)
library(plotly)
library(boldenr)
library(magrittr)
library(leaflet)
library(ggplot2)
library(dplyr)
library(stringr)
library(dash)
library(ECharts2Shiny)
library(sf)

# Step 3. load the functions ####
if(as.vector(Sys.info()["sysname"]) == "Darwin"){
    
    # 1.6 hotspots cases
    source("~/Dropbox/r_developments/r_new_functions/3.Functions/risk_agebs.R")
    
    source("~/Dropbox/r_developments/r_new_functions/3.Functions/risk_map.R")
    
    source("~/Dropbox/r_developments/r_new_functions/3.Functions/hotspots_map.R")
    
    # 1. 7 eggs hotspots ####
    
    source("~/Dropbox/r_developments/r_dashboards/github_pages/test_denv_dash_oax/3.Functions/eggs_hotspots_intensity_map_year.R")

    
} else if(as.vector(Sys.info()["sysname"]) == "Windows"){
    

    # 1.6 hotspots


    # Step  load the risk_ageb function ###
    source("C:/Users/HOME/Dropbox/r_developments/r_new_functions/3.Functions/risk_agebs.R")
    
    # Step  load the risk_map function ####
    source("C:/Users/HOME/Dropbox/r_developments/r_new_functions/3.Functions/risk_map.R")

    # Step  load the hotspots map ####
    source("C:/Users/HOME/Dropbox/r_developments/r_new_functions/3.Functions/hotspots_map.R")
    
    # Step eggs hotspots ####
    source("C:/Users/HOME/Dropbox/r_developments/r_new_functions/3.Functions/eggs_hotspots_intensity_map_year.R")
    
    

    
} else if(as.vector(Sys.info()["sysname"]) == "Linux"){
    
}



# Step 5. Load the RData files ####
if(as.vector(Sys.info()["sysname"]) == "Darwin"){
    # load the blocks
    load("~/OneDrive/automatic_read_ine_2010/8.RData/block_ine10_mx.RData")
    
    # load the dengue cases hotspots
    load("~/Dropbox/hotspots_2021/8.RData/cases_hotspots_agebs19.RData")
    hotspots <- cases_hotspots_agebs19 |>
    sf::st_make_valid()
    
    # load the vector hotspots
    load("~/OneDrive/proyects/hotspots_eggs/8.RData/04/betas/04_campeche_zinb1_betas.RData")
    
    
} else if(as.vector(Sys.info()["sysname"]) == "Windows"){
    
    # Step 1. load the hotspots dengue cases ####
   load("E:/backup/Dropbox_respaldo_2023_01_03/hotspots_2022/8.RData/cases_hotspots_agebs19.RData")
    
    cases_hotspots_agebs19 <- cases_hotspots_agebs19 |>
    sf::st_make_valid()

    
    
    # load the vector hotspots
    load("D:/OneDrive/proyects/hotspots_eggs/8.RData/04_campeche/betas/04_campeche_zinb1_betas.RData")
    
} else if(as.vector(Sys.info()["sysname"]) == "Linux"){
    
}


```

# **Hotspots de la Transmisión de Dengue**

## Column {.tabset}

### [**Campeche**]{style="color:#990000"}

```{r hotspots_dengue_campeche}
hotspots_map(cve_ent = "04",
             locality = "San Francisco de Campeche",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```


### [**Ciudad del Carmen**]{style="color:#990000"}

```{r hotspots_dengue_cd_carmen}
hotspots_map(cve_ent = "04",
             locality = "Ciudad del Carmen",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```

### [**Escárcega**]{style="color:#990000"}

```{r hotspots_dengue_escarcega}
hotspots_map(cve_ent = "04",
             locality = "Escárcega",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```

# **Hotspots del vector de Dengue**

## Column {.tabset}

### [**Campeche**]{style="color:#990000"}

```{r vector_hotspots_campeche, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_04_campeche,
                                 locality = "San Francisco de Campeche",
                                 cve_ent = "04",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```


### [**Ciudad del Carmen**]{style="color:#990000"}

```{r vector_hotspots_cd_carmen, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_04_campeche,
                                 locality = "Ciudad del Carmen",
                                 cve_ent = "04",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### [**Escarcega**]{style="color:#990000"}

```{r vector_hotspots_escarcega, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_04_campeche,
                                 locality = "Escarcega",
                                 cve_ent = "04",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

# **Mapas de Riesgo de Transmisión**

## Column {.tabset}

### [**Campeche**]{style="color:#7d9029"}

```{r, risk_map_campeche, echo=FALSE}
risk <- risk_agebs(spde_model = betas_04_campeche,
                          hotspots = cases_hotspots_agebs19,
                          locality = "San Franciscod de Campeche",
                          cve_ent = "04",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```

### [**Ciudad del Carmen**]{style="color:#7d9029"}

```{r, risk_map_cd_carmen, echo=FALSE}
risk <- risk_agebs(spde_model = betas_04_campeche,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Ciudad del Carmen",
                          cve_ent = "04",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```

### [**Escarcega**]{style="color:#7d9029"}

```{r, risk_map_escarcega, echo=FALSE}
risk <- risk_agebs(spde_model = betas_04_campeche,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Escarcega",
                          cve_ent = "04",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```
