---
title: "Programa de Prevención y Control del Dengue de Yucatán"
output: 
  flexdashboard::flex_dashboard:
      theme: united
      social: ["twitter", "facebook", "menu", "github"]
output_dir: libs      
---

```{r setup}

# Step 1. load the library ####
options(shiny.maxRequestSize=30*1024^2)
library(formattable)
library(tmap)
library(rmarkdown)
library(knitr)
library(shiny)
library(flexdashboard)
library(plotly)
library(boldenr)
library(magrittr)
library(leaflet)
library(ggplot2)
library(dplyr)
library(stringr)
library(dash)
library(ECharts2Shiny)
library(sf)

# Step 3. load the functions ####
if(as.vector(Sys.info()["sysname"]) == "Darwin"){
    
    # 1.6 hotspots cases
    source("~/Dropbox/r_developments/r_new_functions/3.Functions/risk_agebs.R")
    
    source("~/Dropbox/r_developments/r_new_functions/3.Functions/risk_map.R")
    
    source("~/Dropbox/r_developments/r_new_functions/3.Functions/hotspots_map.R")
    
    # 1. 7 eggs hotspots ####
    
    source("~/Dropbox/r_developments/r_dashboards/github_pages/test_denv_dash_oax/3.Functions/eggs_hotspots_intensity_map_year.R")

    
} else if(as.vector(Sys.info()["sysname"]) == "Windows"){
    # 1.1. dengue dataset
    
    # 1.5 ulv dataset
    
    # 1.6 hotspots


    #Step  load the risk_ageb function ###
    source('C:/Users/HOME/Dropbox/r_developments/r_dashboards/github_pages/test_dashboard/3.Functions/risk_agebs.R')

    # Step  load the risk_map function ####
    source("D:/OneDrive/proyects/hotspots/3.Functions/risk_map.R")

    # Step  load the hotspots map ####
    source("C:/Users/HOME/Dropbox/r_developments/r_dashboards/github_pages/test_dashboard/3.Functions/hotspots_map.R")
    
    # 1. 7 eggs hotspots ####
    source("C:/Users/HOME/Dropbox/r_developments/r_dashboards/github_pages/test_denv_dash_oax/3.Functions/eggs_hotspots_intensity_map_year.R")
    
} else if(as.vector(Sys.info()["sysname"]) == "Linux"){
    
}



# Step 5. Load the RData files ####
if(as.vector(Sys.info()["sysname"]) == "Darwin"){
    # load the blocks
    load("~/OneDrive/automatic_read_ine_2010/8.RData/block_ine10_mx.RData")
    
    # load the dengue cases hotspots
    load("~/Dropbox/hotspots_2021/8.RData/cases_hotspots_agebs19.RData")
    hotspots <- cases_hotspots_agebs19 |>
    sf::st_make_valid()
    
    # load the vector hotspots
    load("~/OneDrive/proyects/hotspots_eggs/8.RData/31_yucatan/betas/31_yucatan_zinb1_betas.RData")
    
    
} else if(as.vector(Sys.info()["sysname"]) == "Windows"){
    
    # load the blocks #####
    load("D:/OneDrive/automatic_read_ine_2010/8.RData/block_ine10_mx.RData") 
    
    # Step 1. load the hotspots dengue cases ####
   load("E:/backup/Dropbox_respaldo_2023_01_03/hotspots_2022/8.RData/cases_hotspots_agebs19.RData")
    
    cases_hotspots_agebs19 <- cases_hotspots_agebs19 |>
    sf::st_make_valid()

    
    
    # load the vector hotspots
    load("D:/OneDrive/proyects/hotspots_eggs/8.RData/31_yucatan/betas/31_yucatan_zinb1_betas.RData")
    
} else if(as.vector(Sys.info()["sysname"]) == "Linux"){
    
}


```

# **Hotspots de la Transmisión de Dengue**

## Column {.tabset}

### [**Mérida**]{style="color:#990000"}

<html>

<head>

```{=html}
<style>
body {
  margin: 0px;
}

.wrapper {
    display: grid;
    grid-gap: 2px;
    grid-template-columns: 280px 280px 280px 550px;
    grid-template-rows: 165px 165px 165px 165px;
    background-color: #fff;
    color: "green";
  }

  .box {
    background-color: #cfcfc4;
    color: "green";
    border-radius: 2px;
    padding: 5px;
    font-size: 100%;

  }

  .a {
    grid-column: 1 / 4;
    grid-row: 1 / 4;
  }
  .b {
    grid-column: 4 ;
    grid-row: 1 / 3;
  }
  .c {
    grid-column: 4 ;
    grid-row: 3 / 5 ;
  }
  .d {
    grid-column: 3;
    grid-row: 4;
  }
  .e {
    grid-column: 2;
    grid-row: 4;
  }
  .f {
    grid-column: 1;
    grid-row: 4;
  }
</style>
```
</head>

<body>

::: wrapper
::: {.box .a}
```{r hotspots_dengue_merida}
hotspots_map(cve_ent = "31",
             locality = "Mérida",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```
:::

::: {.box .b}
```{r forest_plot_merida, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# extract the locality

loc <- rgeomex::extract_locality(cve_edo = "31",
                                 locality = "Mérida")

hotspots <- cases_hotspots_agebs19[loc,]
# Logistic Regression
glm.fit <- glm(hotspots_gi ~ DENV_2008 + DENV_2009 +  DENV_2010 + DENV_2011 + 
                   DENV_2012 + DENV_2013  +  DENV_2014 + 
                   DENV_2015  +  DENV_2016  +  DENV_2019 +
                   DENV_2020 + DENV_2021,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                      exponentiate = TRUE)

plotly::ggplotly(plot(result, size_text = 1))
```
:::

::: {.box .c}
```{r power_law_plot_merida,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))

# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto))  |> plotly::layout(showlegend = FALSE)

```
:::

::: {.box .d}
```{r gauge_blocks_merida,fig.align = "center", out.height='100%', out.width = '100%', fig.width= 1.5, fig.height=1}
y_hot <- hotspots |>dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Manzanas",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("success", "warning","danger")))
```
:::

::: {.box .e}
```{r gauge_AGEB_merida, fig.align = "center", out.height='100%', out.width = '100%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("success", "warning","danger")))
```
:::

::: {.box .f}
```{r gauge_casos_merida, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
      dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                   warning = c(6, 10), 
                   danger = c(0, 5),
                   colors = c("success", "warning","danger"))
      )
```
:::
:::

</body>

</html>

### [**Valladolid**]{style="color:#990000"}

<html>

<head>

```{=html}
<style>
body {
  margin: 0px;
}

.wrapper {
    display: grid;
    grid-gap: 2px;
    grid-template-columns: 280px 280px 280px 550px;
    grid-template-rows: 165px 165px 165px 165px;
    background-color: #fff;
    color: "green";
  }

  .box {
    background-color: #cfcfc4;
    color: "green";
    border-radius: 2px;
    padding: 5px;
    font-size: 100%;

  }

  .a {
    grid-column: 1 / 4;
    grid-row: 1 / 4;
  }
  .b {
    grid-column: 4 ;
    grid-row: 1 / 3;
  }
  .c {
    grid-column: 4 ;
    grid-row: 3 / 5 ;
  }
  .d {
    grid-column: 3;
    grid-row: 4;
  }
  .e {
    grid-column: 2;
    grid-row: 4;
  }
  .f {
    grid-column: 1;
    grid-row: 4;
  }
</style>
```
</head>

<body>

::: wrapper
::: {.box .a}
```{r hotspots_dengue_valladolid}
hotspots_map(cve_ent = "31",
             locality = "Valladolid",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```
:::

::: {.box .b}
```{r forest_plot_valladolid, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# extract the locality
loc <- rgeomex::extract_locality(cve_edo = "31",
                                 locality = "Valladolid")

hotspots <- cases_hotspots_agebs19[loc,]
# Logistic Regression
glm.fit <- glm(hotspots_gi ~ DENV_2008 + DENV_2009 +  DENV_2010  + 
                   DENV_2012 + DENV_2013  +  DENV_2014 + 
                   DENV_2015  + DENV_2018+ DENV_2019 +
                   DENV_2020,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                      exponentiate = TRUE)

plotly::ggplotly(plot(result, size_text = 1))
```
:::

::: {.box .c}
```{r power_law_plot_valladolid,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))


# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto))  |> plotly::layout(showlegend = FALSE)

```
:::

::: {.box .d}
```{r gauge_blocks_valladolid,fig.align = "center", out.height='100%', out.width = '100%', fig.width= 1.5, fig.height=1}
y_hot <- hotspots |>dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Manzanas",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("success", "warning","danger")))
```
:::

::: {.box .e}
```{r gauge_AGEB_valladolid, fig.align = "center", out.height='100%', out.width = '100%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("success", "warning","danger")))
```
:::

::: {.box .f}
```{r gauge_casos_valladolid, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                   warning = c(6, 10), 
                   danger = c(0, 5),
                   colors = c("success", "warning","danger"))
      )
```
:::
:::

</body>

</html>

### [**Tizimín**]{style="color:#990000"}

<html>

<head>

```{=html}
<style>
body {
  margin: 0px;
}

.wrapper {
    display: grid;
    grid-gap: 2px;
    grid-template-columns: 280px 280px 280px 550px;
    grid-template-rows: 165px 165px 165px 165px;
    background-color: #fff;
    color: "green";
  }

  .box {
    background-color: #cfcfc4;
    color: "green";
    border-radius: 2px;
    padding: 5px;
    font-size: 100%;

  }

  .a {
    grid-column: 1 / 4;
    grid-row: 1 / 4;
  }
  .b {
    grid-column: 4 ;
    grid-row: 1 / 3;
  }
  .c {
    grid-column: 4 ;
    grid-row: 3 / 5 ;
  }
  .d {
    grid-column: 3;
    grid-row: 4;
  }
  .e {
    grid-column: 2;
    grid-row: 4;
  }
  .f {
    grid-column: 1;
    grid-row: 4;
  }
</style>
```
</head>

<body>

::: wrapper
::: {.box .a}
```{r hotspots_dengue_tizimin}
hotspots_map(cve_ent = "31",
             locality = "Tizimín",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```
:::

::: {.box .b}
```{r forest_plot_tizimin, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# extract the locality

loc <- rgeomex::extract_locality(cve_edo = "31",
                                 locality = "Tizimin")

hotspots <- cases_hotspots_agebs19[loc,]
# Logistic Regression
glm.fit <- glm(hotspots_gi ~  DENV_2009 +  DENV_2010 + DENV_2011 + 
                   DENV_2012 + DENV_2013  +  
                   DENV_2015  +  DENV_2016  + DENV_2018 + DENV_2019,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                      exponentiate = TRUE)

plotly::ggplotly(plot(result, size_text = 1))
```
:::

::: {.box .c}
```{r power_law_plot_tizimin,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))


# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto))  |> plotly::layout(showlegend = FALSE)

```
:::

::: {.box .d}
```{r gauge_blocks_tizimin,fig.align = "center", out.height='100%', out.width = '100%', fig.width= 1.5, fig.height=1}
y_hot <- hotspots |>dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Manzanas",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("success", "warning","danger")))
```
:::

::: {.box .e}
```{r gauge_AGEB_tizimin, fig.align = "center", out.height='100%', out.width = '100%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("success", "warning","danger")))
```
:::

::: {.box .f}
```{r gauge_casos_tizimin, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
      dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                   warning = c(6, 10), 
                   danger = c(0, 5),
                   colors = c("success", "warning","danger"))
      )
```
:::
:::

</body>

</html>

### [**Ticul**]{style="color:#990000"}

<html>

<head>

```{=html}
<style>
body {
  margin: 0px;
}

.wrapper {
    display: grid;
    grid-gap: 2px;
    grid-template-columns: 280px 280px 280px 550px;
    grid-template-rows: 165px 165px 165px 165px;
    background-color: #fff;
    color: "green";
  }

  .box {
    background-color: #cfcfc4;
    color: "green";
    border-radius: 2px;
    padding: 5px;
    font-size: 100%;

  }

  .a {
    grid-column: 1 / 4;
    grid-row: 1 / 4;
  }
  .b {
    grid-column: 4 ;
    grid-row: 1 / 3;
  }
  .c {
    grid-column: 4 ;
    grid-row: 3 / 5 ;
  }
  .d {
    grid-column: 3;
    grid-row: 4;
  }
  .e {
    grid-column: 2;
    grid-row: 4;
  }
  .f {
    grid-column: 1;
    grid-row: 4;
  }
</style>
```
</head>

<body>

::: wrapper
::: {.box .a}
```{r hotspots_dengue_ticul}
hotspots_map(cve_ent = "31",
             locality = "Ticul",
             hotspots = cases_hotspots_agebs19,
             static_map = FALSE)

```
:::

::: {.box .b}
```{r forest_plot_ticul, dpi = 300, fig.height= 5,fig.width = 7,fig.align = "center", out.height='100%', out.width = '100%',fig.show = "hold"}
 
# extract the locality

loc <- rgeomex::extract_locality(cve_edo = "31",
                                 locality = "Ticul")

hotspots <- cases_hotspots_agebs19[loc,]
# Logistic Regression
glm.fit <- glm(hotspots_gi ~  DENV_2009 +  DENV_2010 + DENV_2011 + 
                   DENV_2012 + DENV_2013  +  DENV_2014 +
                   DENV_2016  + DENV_2018 + DENV_2019 + DENV_2020,
               data = hotspots, 
               family = binomial)

result <- parameters::model_parameters(glm.fit, 
                                      exponentiate = TRUE)

plotly::ggplotly(plot(result, size_text = 1))
```
:::

::: {.box .c}
```{r power_law_plot_ticul,dpi = 300, warning=FALSE, fig.align = "center", out.width = '100%',out.height='100%',fig.show = "hold"}
# Step 7. make the function por calculate the cumulative ####
funcumsum <- function(x){
    x$cumulative_n <- cumsum(x$n_cases)
    x$perc_cumsum_n <- round((cumsum(x$n_cases)/sum(x$n_cases))*100, digits = 1)
    #x$cumulative_ha <- cumsum(x$ha)
    #x$perc_cumsum_ha <- round((cumsum(x$ha)/sum(x$ha))*100, digits = 1)
    x$id <- 1
    x$id_cumsum <- cumsum(x$id)
    x$id_perc_cum <- round((cumsum(x$id)/nrow(x))*100, digits = 1)
    x
}
# step 8.
data_pareto <- hotspots   |>
    # sf::st_drop_geometry()  |>
    # dplyr::mutate(n_cases = rowSums(dplyr::select(., dplyr::starts_with("DENV"))),
    #              loc = "locality")
    #dplyr::mutate(n_cases = rowSums(dplyr::across(DENV_2008:DENV_2021)),
    #              loc = "locality")  |>
    dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    
    dplyr::select(loc, n_cases, hotspots_gi)  |>
    dplyr::arrange(loc, desc(hotspots_gi), desc(n_cases))  |>
    dplyr::group_by(loc)  |>
    tidyr::nest()  |>
    dplyr::mutate(pareto_cases = purrr::map(data,
                                            funcumsum))  |>
    dplyr::select(-data)  |>
    tidyr::unnest(cols = c(pareto_cases))


# step 4. visualization of pareto rules 
plotly::ggplotly(denhotspots::power_law_plot(x = data_pareto))  |> plotly::layout(showlegend = FALSE)

```
:::

::: {.box .d}
```{r gauge_blocks_ticul,fig.align = "center", out.height='100%', out.width = '100%', fig.width= 1.5, fig.height=1}
y_hot <- hotspots |>dplyr::filter(hotspots_gi == 1)
centroid <- rgeomex::blocks_ine20_mx_centroid |>
  sf::st_as_sf(coords = c("x", "y"), crs = 4326)
b_loc <- centroid[hotspots, ]
b_hot <- b_loc[y_hot, ]
flexdashboard::gauge(round((nrow(b_hot)/nrow(b_loc))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Manzanas",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("success", "warning","danger")))
```
:::

::: {.box .e}
```{r gauge_AGEB_ticul, fig.align = "center", out.height='100%', out.width = '100%'}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)
  
flexdashboard::gauge(round((nrow(y_hot)/nrow(y))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "AGEBs",
      flexdashboard::gaugeSectors(success = c(0, 30), 
                                  warning = c(31, 50), 
                                  danger = c(51, 100),
                                  colors = c("success", "warning","danger")))
```
:::

::: {.box .f}
```{r gauge_casos_ticul, out.height='90%', out.width = '90%', fig.align = "center"}

y <- hotspots  |>
    sf::st_drop_geometry() |>
     dplyr::mutate(n_cases = rowSums(dplyr::across(dplyr::starts_with("DENV"))),
                  loc = "locality") |>
    dplyr::select(loc, n_cases, hotspots_gi) 
y_hot <- y |>dplyr::filter(hotspots_gi == 1)

flexdashboard::gauge(round((sum(y_hot$n_cases)/sum(y$n_cases))*100, digits = 1),
      min = 0, max = 100, 
      symbol = '%', 
      label = "Casos de Dengue",
      flexdashboard::gaugeSectors(success = c(11, 100), 
                   warning = c(6, 10), 
                   danger = c(0, 5),
                   colors = c("success", "warning","danger"))
      )
```
:::
:::

</body>

</html>

# **Hotspots del Vector del Dengue**

## Column {.tabset}

### [**Mérida**]{style="color:#990000"}

```{r vector_hotspots_merida, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_31_yucatan,
                                 locality = "Mérida",
                                 cve_ent = "31",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### [**Hunucmá**]{style="color:#990000"}

```{r vector_hotspots_hunucma, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_31_yucatan,
                                 locality = "Hunucma",
                                 cve_ent = "31",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### [**Progreso**]{style="color:#990000"}

```{r vector_hotspots_propreso, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_31_yucatan,
                                 locality = "Progreso",
                                 cve_ent = "31",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### [**Motul**]{style="color:#990000"}

```{r vector_hotspots_motul, dpi = 300, warning=FALSE, message=FALSE, error=FALSE}

eggs_hotspots_intensity_map_year(betas = betas_31_yucatan,
                                 locality = "Motul de Carrillo Puerto",
                                 cve_ent = "31",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### [**Valladolid**]{style="color:#990000"}

```{r vector_hotspots_valladolid, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_31_yucatan,
                                 locality = "Valladolid",
                                 cve_ent = "31",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### [**Tizimin**]{style="color:#990000"}

```{r vector_hotspots_tizimin, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_31_yucatan,
                                 locality = "Tizimin",
                                 cve_ent = "31",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### [**Ticul**]{style="color:#990000"}

```{r vector_hotspots_ticul, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_31_yucatan,
                                 locality = "Ticul",
                                 cve_ent = "31",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### [**Tekax**]{style="color:#990000"}

```{r vector_hotspots_tekax, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_31_yucatan,
                                 locality = "Tekax de Alvaro Obregon",
                                 cve_ent = "31",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

### [**Peto**]{style="color:#990000"}

```{r vector_hotspots_peto, dpi = 300, warning=FALSE, message=FALSE}
eggs_hotspots_intensity_map_year(betas = betas_31_yucatan,
                                 locality = "Peto",
                                 cve_ent = "31",
                                 palette = rcartocolor::carto_pal,
                                 name = "SunsetDark")
```

# **Dengue Risk Maps**

## Column {.tabset}

### [**Mérida**]{style="color:#7d9029"}

```{r, risk_map_merida, echo=FALSE}
risk <- risk_agebs(spde_model = betas_31_yucatan,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Mérida",
                          cve_ent = "31",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```

### [**Valladolid**]{style="color:#7d9029"}

```{r, risk_map_valladolid, echo=FALSE}
risk <- risk_agebs(spde_model = betas_31_yucatan,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Valladolid",
                          cve_ent = "31",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```

### [**Tizimín**]{style="color:#7d9029"}

```{r, risk_map_tizimin, echo=FALSE}
risk <- risk_agebs(spde_model = betas_31_yucatan,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Tizimín",
                          cve_ent = "31",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```

### [**Ticul**]{style="color:#7d9029"}

```{r, risk_map_ticul, echo=FALSE}
risk <- risk_agebs(spde_model = betas_31_yucatan,
                          hotspots = cases_hotspots_agebs19,
                          locality = "Ticul",
                          cve_ent = "31",
                          intensity_perc = 25)
risk_map(risk = risk, staticmap = FALSE)
```
